\documentclass[11pt, a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{mdframed}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds}

% --- colour palette (phosphor green theme) ---
\definecolor{phosphor}{RGB}{20, 200, 20}
\definecolor{dimgreen}{RGB}{10, 120, 10}
\definecolor{darkbg}{RGB}{8, 20, 8}
\definecolor{accentcyan}{RGB}{0, 180, 220}
\definecolor{accentred}{RGB}{220, 40, 20}
\definecolor{tabhead}{RGB}{20, 60, 20}
\definecolor{rowalt}{RGB}{230, 245, 230}
\definecolor{notebg}{RGB}{240, 250, 240}

% --- hyperref ---
\hypersetup{
  colorlinks = true,
  linkcolor  = dimgreen,
  urlcolor   = accentcyan,
  citecolor  = dimgreen,
}

% --- header / footer ---
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{dimgreen}{OAMP — Development Roadmap}}
\fancyhead[R]{\small\textcolor{dimgreen}{Phases 1--5 + stretch}}
\fancyfoot[C]{\small\textcolor{dimgreen}{\thepage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{dimgreen}\leaders\hrule height \headrulewidth\hfill}}

% --- section styling ---
\titleformat{\section}{\large\bfseries\color{dimgreen}}{}{0em}{}[\textcolor{dimgreen}{\titlerule[0.6pt]}]
\titleformat{\subsection}{\normalsize\bfseries\color{dimgreen!80!black}}{}{0em}{}
\titleformat{\subsubsection}{\normalsize\itshape\color{dimgreen!70!black}}{}{0em}{}

% --- note box ---
\newmdenv[
  backgroundcolor=notebg,
  linecolor=dimgreen,
  linewidth=1pt,
  leftmargin=0pt, rightmargin=0pt,
  innerleftmargin=10pt, innerrightmargin=10pt,
  innertopmargin=6pt, innerbottommargin=6pt,
]{notebox}

% --- table helpers ---
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\begin{document}

% ============================================================
%  TITLE
% ============================================================
\begin{titlepage}
  \pagecolor{darkbg}
  \color{phosphor}
  \vspace*{3cm}
  \begin{center}
    {\Huge\bfseries Open Source Astrodynamic\\[0.3em]
     Mission Planning}\\[1.5em]
    {\LARGE\color{accentcyan} Development Roadmap}\\[0.8em]
    {\large Phases 1--5 + Stretch Goals}\\[3cm]
    \textcolor{phosphor!60!black}{\rule{0.5\textwidth}{0.4pt}}\\[1em]
    {\normalsize
      Precision Newtonian \quad\textbullet\quad CR3BP \&
      Low-Energy Transfers \quad\textbullet\quad\\[0.2em]
      Star Field \& Astro-Navigation \quad\textbullet\quad GR (stretch)}\\[2em]
    {\small\color{phosphor!60!black}
      AGPL-3.0 \quad|\quad HortDog \quad|\quad \today}
  \end{center}
\end{titlepage}

\pagecolor{white}
\color{black}

% ============================================================
%  TABLE OF CONTENTS
% ============================================================
\tableofcontents
\newpage

% ============================================================
%  EXECUTIVE SUMMARY
% ============================================================
\section{Executive Summary}

Phase~1 delivered the project skeleton: a Newtonian $+$~J2 propagator with
DOP853 integration, an open-loop launch simulator, a SPICE kernel wrapper with
reproducibility-locked manifests, and a WebGPU~3D viewer showing three orbital
scenarios.

\textbf{Phase~2} (\emph{shipped}) keeps the physics Newtonian but raises the
fidelity to the level needed for real mission design: higher-order gravity
(J2--J6), atmospheric drag (exponential + MSIS), solar radiation pressure,
third-body perturbations, symplectic integrators (Verlet, Yoshida-4),
finite-burn modelling, TLE ingest, a Lambert / CasADi trajectory optimizer,
NDJSON streaming, and a full manoeuvre-editor frontend.

\textbf{Phase~3} (\emph{shipped}) brings every backend capability to the
sandbox frontend (J2--J6, drag with MSIS, SRP, third-body Moon/Sun, finite
burns, four solver panels covering Hohmann/Lambert/multi-burn NLP/TLE), adds
a central-body selector with full Moon support (canonical $\mu$, $R$, $J_n$,
$\omega$), wires SPICE ephemerides into the renderer as a secondary-body
wireframe, and ties it together with an end-to-end cislunar TLI demo.

\textbf{Phase~4} (\emph{shipped}) extends the dynamics layer with the
circular-restricted three-body problem (CR3BP), Lagrange-point computation,
planar Lyapunov periodic orbits via differential correction, invariant
manifold tubes, EM-synodic rotating-frame visualization, and the
weak-stability-boundary (WSB) capture diagnostic --- the foundations for
low-energy transfers and ballistic capture into lunar orbit.

\textbf{Mission-planner polish} (\emph{shipped}) wraps the editor:
preset-orbit library (ISS/LEO/SSO/GTO/GEO/Molniya/lunar/halo-seeds), orbital
elements editor, integrator + epoch + SPICE-status controls, live $\Sigma|\Delta v|$
budget, save / load mission JSON, autosave to \texttt{localStorage}, CSV
trajectory export, multi-burn inertial$\to$RIC auto-conversion, event-timeline
strip, in-editor Lyapunov / WSB / launch sub-panels, animated time scrub with
solid past / dashed future, real Natural Earth coastline overlay.

\textbf{Phase~5} (\emph{next}) renders a real \textbf{star field} from the
Hipparcos / Yale Bright Star catalogue and adds \textbf{astro-navigation}:
star-tracker simulation, lost-in-space attitude solvers, optical landmark
navigation, and a closed-loop ``navigate by stars'' demo.

\textbf{Future / Stretch Goals} keep the door open for ambitious follow-ups:
post-Newtonian and full General Relativity propagation (BCRS geodesics,
tetrad thrust, Ray-backed metric pre-bake cache), tesseral gravity, ground
tracks / visibility analysis, conjunction analysis against TLE catalogues.

\textbf{``Let your creativity go wild''} closes the document with a
deliberately open-ended list of blue-sky directions --- tour mode, live
ISS tracking, generative trajectory design, asteroid mining, solar sails,
WebXR, audio synthesis, alternate-physics sandboxes --- where the only
constraint is ``it should be cool.''

\begin{notebox}
\textbf{Convention lock:}
UTC ISO-8601 on the wire; TDB seconds since J2000 (= SPICE ET) internally.
All SI units in the engine.
\textbf{Licence: AGPL-3.0} (switched from Apache-2.0 in Phase~4 polish;
network-service deployments inherit source-disclosure obligations).
SPICE kernels and the Natural Earth coastline are now tracked in-tree so a
fresh clone runs with zero network fetches.
\end{notebox}

% ============================================================
%  PHASE 2
% ============================================================
\newpage
\section{Phase 2 — Precision Newtonian \& Mission Design}

\subsection{Goals}

A mission designer should be able to: load a TLE or specify an initial state,
apply atmospheric drag and solar radiation pressure, add impulsive $\Delta v$
burns, solve a Lambert transfer or run a fuel-optimal CasADi optimisation, and
watch the result stream live in the 3D viewer.

\subsection{2a — Dynamics Fidelity}

\subsubsection{Higher-Order Gravity}

Extend \texttt{oamp.dynamics.newtonian} with zonal harmonics $J_3$--$J_6$
(Vallado §8.7). The acceleration from $J_n$ is:

\begin{equation}
  \mathbf{a}_{J_n} = -\frac{\mu}{r^2} \frac{n+1}{2}
    \left(\frac{R_\oplus}{r}\right)^n J_n \,
    \nabla P_n(\sin\phi)
\end{equation}

where $P_n$ is the Legendre polynomial and $\phi$ the geocentric latitude.
Tesseral ($C_{nm}$, $S_{nm}$) terms are planned but deferred to Phase~2b+.

\subsubsection{Atmospheric Drag}

Replace the exponential density model in \texttt{launch.py} with
NRLMSISE-00 via the \texttt{nrlmsise00} Python package. The drag acceleration
is:

\begin{equation}
  \mathbf{a}_\text{drag} = -\tfrac{1}{2}\, \rho(h)\, C_D\, \frac{A}{m}\,
    |\mathbf{v}_\text{rel}|\,\mathbf{v}_\text{rel}
\end{equation}

where $\mathbf{v}_\text{rel}$ accounts for Earth's rotation
($\boldsymbol{\omega}_\oplus \times \mathbf{r}$). Vehicle cross-section $A$
and $C_D$ are added to the propagation request body.

\subsubsection{Solar Radiation Pressure}

Cannonball model with cylindrical shadow cones for Earth and Moon:

\begin{equation}
  \mathbf{a}_\text{SRP} = \nu \frac{P_\odot}{c}
    \frac{A_\text{eff}}{m} \hat{\mathbf{r}}_{\odot}
\end{equation}

where $\nu \in [0,1]$ is the shadow function (computed via SPICE body
positions already available) and $P_\odot = 4.56\times10^{-6}$~N~m$^{-2}$
at 1~AU.

\subsubsection{Third-Body Gravity}

Moon and Sun perturbations using SPICE \texttt{body\_state()} (already
implemented) with point-mass attractions and the indirect term:

\begin{equation}
  \mathbf{a}_\text{3b} = \sum_k \mu_k
    \left(\frac{\mathbf{r}_k - \mathbf{r}}{|\mathbf{r}_k - \mathbf{r}|^3}
          - \frac{\mathbf{r}_k}{|\mathbf{r}_k|^3}\right)
\end{equation}

\subsubsection{Symplectic Integrator}

Add SABA2 (symplectic Birkhoff--Adams) alongside DOP853 for long-arc
propagation where energy conservation over months matters more than step-size
adaptivity. Selectable via \texttt{integrator: "dop853" | "saba2"} in the
request.

\subsubsection{New API Flags}

\begin{center}
\begin{tabular}{L{3cm} L{4cm} L{5cm}}
  \toprule
  \textbf{Field} & \textbf{Type} & \textbf{Effect} \\
  \midrule
  \texttt{drag}       & \texttt{bool}        & NRLMSISE-00 drag \\
  \texttt{srp}        & \texttt{bool}        & Solar radiation pressure \\
  \texttt{third\_body}& \texttt{list[str]}   & Bodies e.g.\ \texttt{["moon","sun"]} \\
  \texttt{jn\_max}    & \texttt{int}         & Max zonal harmonic (2–6) \\
  \texttt{integrator} & \texttt{str}         & \texttt{"dop853"} or \texttt{"saba2"} \\
  \texttt{vehicle}    & \texttt{VehicleModel}& $m$, $A$, $C_D$, $C_R$ \\
  \bottomrule
\end{tabular}
\end{center}

\subsubsection{Tests}

\begin{itemize}[noitemsep]
  \item Energy drift $< 10^{-9}$ relative over 30-day arc (SABA2)
  \item Nodal regression matches NRLMSISE drag prediction within 5\%
  \item SRP produces correct signature in inclination evolution
  \item Moon third-body matches SPICE-derived perturbation to $< 1$~m/day
\end{itemize}

\subsection{2b — TLE Ingest}

Add \texttt{GET /tle?norad=\{id\}} which:
\begin{enumerate}[noitemsep]
  \item Fetches the current TLE from Celestrak
  \item Parses with \texttt{sgp4} (already evaluable from \texttt{conda-forge})
  \item Propagates to epoch via SGP4
  \item Converts mean-element state to osculating Cartesian (Brouwer transform)
  \item Returns an \texttt{InitialState} compatible with \texttt{POST /propagate}
\end{enumerate}

A manifest of pinned test TLEs (NORAD ID + epoch + expected state checksum)
mirrors the SPICE kernel manifest pattern for reproducible CI.

\subsection{2c — $\Delta v$ Manoeuvre Engine}

\subsubsection{Data Model}

\begin{verbatim}
class Maneuver(BaseModel):
    t_tdb: float                # TDB seconds since J2000
    dv_ric: list[float]         # [radial, in-track, cross-track], m/s
\end{verbatim}

\texttt{POST /propagate} accepts an optional \texttt{maneuvers: list[Maneuver]};
the integrator applies instantaneous velocity kicks at each epoch by
transforming RIC $\to$ ECI and restarting the ODE.

\subsubsection{Analytical Solvers}

\begin{center}
\begin{tabular}{L{3.5cm} L{9cm}}
  \toprule
  \textbf{Endpoint} & \textbf{Description} \\
  \midrule
  \texttt{POST /optimize/hohmann}  &
    Closed-form two-impulse Hohmann transfer. Returns $\Delta v_1$,
    $\Delta v_2$, transfer time. \\[4pt]
  \texttt{POST /optimize/lambert}  &
    Universal-variable Lambert solver (Izzo/Gooding algorithm) for
    arbitrary two-point boundary-value transfer. \\
  \bottomrule
\end{tabular}
\end{center}

\subsubsection{Numerical Optimiser}

\texttt{POST /optimize/trajectory} uses CasADi (already in the \texttt{default}
pixi environment) to solve the fuel-optimal NLP:

\begin{equation}
  \min_{\{\Delta \mathbf{v}_k\}} \sum_k |\Delta \mathbf{v}_k|
  \quad \text{s.t.} \quad
  \mathbf{x}_{k+1} = \phi(\mathbf{x}_k + \Delta\mathbf{v}_k,\, \Delta t_k),\;
  \mathbf{x}_N = \mathbf{x}_\text{target}
\end{equation}

The propagation $\phi$ is the DOP853 integrator wrapped as a CasADi callback.
Warm-starting from the Lambert solution typically converges in $< 30$~iterations.

\subsection{2d — Real-time WebSocket Streaming}

Replace the echo-only \texttt{/ws} channel with a streaming propagator. The
protocol uses msgpack (already a dependency):

\begin{enumerate}[noitemsep]
  \item Client sends \texttt{\{scenario\_id, t\_start, t\_end, dt, config\}}
  \item Server propagates in chunks of $N$ steps on a Ray actor (or asyncio for
        small jobs)
  \item Each chunk is msgpack-encoded and sent as a binary WebSocket frame
  \item A terminal \texttt{\{done: true, elapsed\_ms\}} frame closes the stream
\end{enumerate}

This enables the frontend time-scrubber to show live progress for long
multi-day propagations.

\subsection{2e — Frontend}

\begin{center}
\begin{tabularx}{\textwidth}{L{3.5cm} X}
  \toprule
  \textbf{Feature} & \textbf{Detail} \\
  \midrule
  Manoeuvre editor &
    Click on trajectory to insert a burn node; drag the arrow glyph to adjust
    $\Delta v$ magnitude and direction in the RIC frame. \\[4pt]
  Time scrubber &
    Slider replays the trajectory; a spacecraft marker moves along the path.
    Shows $t_\text{UTC}$, $r$, $v$, and remaining $\Delta v$ budget. \\[4pt]
  Multi-trajectory overlay &
    Compare baseline vs optimised trajectories side-by-side with per-trajectory
    colour coding and a difference-norm plot in a side panel. \\[4pt]
  Velocity / thrust vectors &
    Short arrow glyphs at the spacecraft position; length proportional to
    $|\mathbf{v}|$ or $|\mathbf{f}|$ with configurable scale. \\[4pt]
  WebGL2 fallback &
    2D ground-track canvas (equirectangular) for browsers without WebGPU.
    Uses the same trajectory data from the REST API. \\[4pt]
  Scenario save/load &
    JSON export of full mission state (initial conditions, manoeuvres,
    vehicle model, propagation config). Drag-and-drop import. \\
  \bottomrule
\end{tabularx}
\end{center}

\subsection{Phase 2 Sequencing}

\begin{center}
\begin{tabular}{L{5cm} C{2.5cm} L{5.5cm}}
  \toprule
  \textbf{Work item} & \textbf{Est.\ duration} & \textbf{Dependency} \\
  \midrule
  2a Drag + third-body     & 2--3 weeks & Phase 1 \\
  2b TLE ingest            & 1 week     & Phase 1 \\
  2c Lambert + CasADi NLP  & 2--3 weeks & 2a \\
  2d WebSocket streaming   & 1 week     & Phase 1 \\
  2e Frontend              & 3--4 weeks & 2c, 2d (parallel) \\
  \midrule
  \textbf{Total}           & \textbf{9--12 weeks} & \\
  \bottomrule
\end{tabular}
\end{center}

% ============================================================
%  PHASE 3 — Sandbox Integration & Lunar System (SHIPPED)
% ============================================================
\newpage
\section{Phase 3 — Sandbox Integration \& Lunar System}

\subsection{Goals}

Make every backend capability visible and editable in the WebGPU sandbox,
extend the central-body abstraction to the Moon, and use SPICE ephemerides
to render the Moon at its inertial position --- producing an end-to-end
cislunar transfer demo that exercises the full Phase~2 stack
(higher-order gravity, third-body perturbation, finite burns, Lambert).

\subsection{3.1 — Perturbation editor expansion (shipped)}

The maneuver editor sidebar gained a full Perturbations section exposing
every flag the backend already accepts:

\begin{itemize}[leftmargin=*]
  \item Zonal harmonics dropdown ($J_2$\,\dots\,$J_6$) bound to
        \texttt{PropagateRequest.jn\_max}
  \item Atmospheric drag with model selector
        (\texttt{exponential} \,|\, \texttt{msis}); vehicle inputs share
        a single section
  \item Solar radiation pressure (cannonball) with $C_r$, area
  \item Third-body checkboxes for Moon and Sun
        (forwarded as \texttt{third\_body: ["MOON", "SUN"]})
  \item Live ``active forces'' readout displaying what the server actually
        applied (\texttt{response.perturbations[]})
\end{itemize}

\subsection{3.2 — Solver panel (shipped)}

A single sidebar section with a solver-type dropdown and a dynamically
rendered form:

\begin{center}
\rowcolors{2}{rowalt}{white}
\begin{tabularx}{\textwidth}{>{\bfseries}l X X}
  \rowcolor{tabhead}\color{white}\textbf{Solver}
    & \color{white}\textbf{Inputs}
    & \color{white}\textbf{Loads into editor} \\
  Hohmann       & $r_1$, $r_2$, $\mu$
                & 2 impulsive maneuvers, IC at LEO \\
  Lambert       & $\vec r_1$, $\vec r_2$, TOF
                & IC = $(\vec r_1, \vec v_1^{\text{Lambert}})$, duration $=$ TOF \\
  Multi-burn NLP & $N$ epochs, target $\vec r_f, \vec v_f$
                & Δv list + convergence stats (inertial; displayed) \\
  TLE           & NORAD ID \emph{or} line1/line2 (+ \texttt{at\_utc})
                & ECI state at epoch, period auto-set \\
\end{tabularx}
\end{center}

Each solver writes results back to \texttt{editorState} and auto-propagates,
so the user sees the orbit immediately.

\subsection{3.3 — Central-body selector + lunar constants}

\texttt{PropagateRequest.body\_name: "EARTH" | "MOON" | "SUN"} resolves to
the canonical \texttt{Body} constant (correct $\mu$, $R$, $J_n$, $\omega$);
the legacy \texttt{mu}/\texttt{body\_radius} fields are kept for back-compat.
Lunar zonal harmonics $J_2$\,\dots\,$J_6$ are populated from the GRGM1200A
low-order solution. The frontend dropdown repopulates the initial state
with a sensible low circular orbit at the body's default altitude and
clears drag/SRP (which require an atmosphere).

\subsection{3.4 — Moon rendering}

The WebGPU renderer gained \texttt{setSecondaryBody(position, radius, color)}:
a low-resolution wireframe sphere translated to the inertial Moon position.
A new endpoint \texttt{POST /spice/ephemeris} accepts a list of TDB-second
offsets from a UTC epoch and returns the corresponding body states ---
batching what \texttt{/spice/state} did for a single time. The frontend
samples Moon positions at $\sim$60 points across the active trajectory and
advances the Moon as the time scrubber moves (binary-search lookup).

\subsection{3.5 — Cislunar TLI demo}

A top-bar button that ties the whole stack together:

\begin{enumerate}[leftmargin=*]
  \item Query Moon position at the demo epoch from SPICE
  \item Solve Lambert: $200\,$km LEO $\to$ Moon position in $3.5\,$d
  \item Load TLI Δv as an impulsive RIC maneuver
  \item Propagate with $J_2$ + third-body Moon
  \item Render trajectory + Moon wireframe + apse markers
\end{enumerate}

Graceful degradation: if SPICE kernels aren't loaded the status bar prompts
the user to run \texttt{pixi run kernels} rather than failing silently.

\subsection{3.6 — Polish}

\begin{itemize}[leftmargin=*]
  \item \textbf{Camera}: adaptive near/far ($0.005 \cdot d \dots 500 \cdot d$)
        keeps \texttt{depth24plus} precision usable across the whole zoom
        range; wheel-zoom band expanded to
        $10^{-3} \dots 10^4$ scene units
  \item \textbf{Camera target switching}: orbit-camera target switchable
        between central body / spacecraft / Moon via a footer dropdown
  \item \textbf{Apse markers}: tiny magenta/yellow crosses at periapsis /
        apoapsis. Detection via $\dot r$ zero-crossings (not triplet
        extremum) and suppressed when
        $(r_\text{max} - r_\text{min}) / \bar r < 10^{-3}$ to avoid spurious
        markers on near-circular orbits
  \item \textbf{Altitude chart}: $|\vec r|(t)$ polyline in the footer with
        a vertical cursor that tracks the time scrubber
\end{itemize}

\subsection{3.x — Known limitations}

\begin{itemize}[leftmargin=*]
  \item Multi-burn NLP returns inertial $\Delta v$; the editor speaks RIC,
        so it displays results rather than round-tripping. A future
        \texttt{dv\_inertial} field on the Maneuver model would close this.
  \item Moon ephemeris is sampled only at the configured demo epoch
        (\texttt{2026-01-01T00:00:00}); a per-trajectory configurable
        $t_0$ is a small follow-up.
  \item Frame is always inertial J2000. Phase~4 introduces the
        synodic-frame option needed for periodic-orbit analysis.
\end{itemize}

\subsection{3 — Status \& tests}

All 43 backend tests pass; ruff clean; frontend type-check clean.

% ============================================================
%  PHASE 4 — CR3BP, Lagrange points, low-energy transfers
% ============================================================
\newpage
\section{Phase 4 — Rotating Frames, CR3BP \& Low-Energy Transfers}

\subsection{Goals}

Add the dynamics, frames, and visualization needed to design and visualize
\emph{low-energy} (manifold-guided) transfers and \emph{ballistic capture}
trajectories. The Newtonian path remains the fast default; CR3BP is opt-in
via a frame selector and a separate propagator family.

The deliverable is: ``the user can pick an Earth--Moon halo orbit by energy,
see the unstable manifold tube reaching Earth, and choose an initial state
on that tube that ballistically captures into a low lunar orbit.''

\subsection{Pillar A --- Frame infrastructure}

\subsubsection{4.1 Frame definitions}

A \texttt{Frame} dataclass in \texttt{backend/oamp/frames.py} (new file)
with time-dependent rotation + translation:

\begin{itemize}[leftmargin=*]
  \item \textbf{J2000}: inertial (current default)
  \item \textbf{EM\_SYNODIC}: rotating with the Earth--Moon line, origin at
        the system barycenter --- the Moon and Earth are stationary
  \item \textbf{SE\_SYNODIC}: rotating with the Sun--Earth line; required
        for Weak-Stability-Boundary transfers
  \item \textbf{BCI\_EARTH} / \textbf{BCI\_MOON}: body-centered J2000
  \item \textbf{BCR\_*}: body-centered rotating, surface-relative
\end{itemize}

Each conversion is a $3{\times}3$ rotation $R(t)$ plus an origin
translation $\Delta\vec r(t)$, plus the velocity correction
$\vec v' = R(\vec v - \boldsymbol\omega \times \vec r) - \dot{\Delta\vec r}$.

\subsubsection{4.2 Frame-aware propagator and visualization}

\begin{itemize}[leftmargin=*]
  \item \texttt{PropagateRequest.output\_frame} --- backend transforms the
        result before returning
  \item \texttt{POST /transform/states} --- standalone batch transform
        endpoint
  \item Frontend frame selector dropdown coupled to \texttt{output\_frame}
        and to the renderer's ``what is at origin''
\end{itemize}

\subsection{Pillar B --- CR3BP dynamics}

\subsubsection{4.3 CR3BP propagator}

Non-dimensional equations of motion in the synodic frame with mass ratio
$\mu = m_2/(m_1+m_2)$.  In file
\texttt{backend/oamp/dynamics/cr3bp.py}.  JAX-friendly RHS so we can JIT
and \texttt{vmap} for batch trajectory studies (this links to the GPU
acceleration work):

\begin{equation}
  \begin{aligned}
    \ddot x &= \phantom{-}2\dot y + x - (1-\mu)\frac{x+\mu}{r_1^3} - \mu\frac{x-1+\mu}{r_2^3} \\
    \ddot y &= -2\dot x + y - (1-\mu)\frac{y}{r_1^3} - \mu\frac{y}{r_2^3} \\
    \ddot z &= - (1-\mu)\frac{z}{r_1^3} - \mu\frac{z}{r_2^3}
  \end{aligned}
\end{equation}

\subsubsection{4.4 Lagrange points + Jacobi constant}

\begin{itemize}[leftmargin=*]
  \item Newton solve for collinear $L_1, L_2, L_3$ from the quintic;
        exact for triangular $L_4, L_5$
  \item \texttt{jacobi\_constant(state, $\mu$)} as a pseudo-energy invariant;
        conserved to $\sim 10^{-10}$ over a closed periodic orbit, useful
        as an integration-error gauge
  \item Endpoint \texttt{GET /cr3bp/lagrange?mu=...}
\end{itemize}

\subsubsection{4.5 Periodic orbit families (hardest single item)}

\begin{itemize}[leftmargin=*]
  \item Planar Lyapunov around $L_1, L_2$ --- linearised initial guess
        + differential correction (Newton on the period-crossing residual)
  \item 3D halo orbits --- Richardson 3rd-order analytical seed, then
        differential correction
  \item Vertical Lyapunov (out-of-plane)
  \item \textbf{Family continuation}: pseudo-arclength on energy/period to
        walk along a family
  \item Endpoint
        \texttt{POST /cr3bp/periodic-orbit \{type, L, energy\}}
\end{itemize}

\subsubsection{4.6 Invariant manifolds}

\begin{itemize}[leftmargin=*]
  \item Monodromy matrix $\Phi(T)$ around a periodic orbit
  \item Eigendecomposition $\to$ stable ($|\lambda|<1$) and unstable
        ($|\lambda|>1$) directions
  \item Integrate the stable manifold backward and the unstable manifold
        forward from a sampling of points along the orbit
        ($\sim$100 trajectories typical)
  \item Endpoint
        \texttt{POST /cr3bp/manifold \{orbit, direction, branch, duration\}}
\end{itemize}

\subsection{Pillar C --- Low-energy transfers}

\subsubsection{4.7 Manifold-guided transfers}

\begin{itemize}[leftmargin=*]
  \item \textbf{Earth--Moon $L_1/L_2$ transit}: depart LEO $\to$ unstable
        manifold of $L_1/L_2$ halo $\to$ arrive at the lunar SOI without
        a capture burn
  \item \textbf{WSB (Belbruno) transfer}: depart Earth $\to$ Sun--Earth
        manifold tube $\to$ swing through Sun--Earth $L_1/L_2$ $\to$ arrive
        at Earth--Moon $L_2$ manifold $\to$ ballistic capture into lunar
        orbit. $\sim$90--110~d TOF, $\sim$10--20\% $\Delta v$ savings vs.\
        Hohmann (Hiten, GRAIL, LADEE precedent).
  \item Endpoint
        \texttt{POST /transfer/low-energy \{depart, target, type\}}
\end{itemize}

\subsubsection{4.8 Ballistic-capture diagnostic}

Sample many initial conditions near the lunar $L_1/L_2$ manifolds, propagate
backward in the BCR4BP (Sun perturbation included), classify each as
``captured'' (lunar bound for $\ge 3$ months) or ``escapes''. The boundary
between these classes is the \textbf{Weak Stability Boundary}.  Visualize as
a colour-coded map in the synodic frame --- the iconic Belbruno plot.

\subsection{Pillar C visualization}

\subsubsection{4.9 Frontend integration}

\begin{itemize}[leftmargin=*]
  \item Frame selector coupled to \texttt{output\_frame} on every propagate
        call; renderer ``central body'' becomes the barycenter when synodic
  \item $L_1$\,\dots\,$L_5$ markers (small $\times$ glyphs) drawn at their
        synodic-frame positions
  \item Periodic-orbit catalogue browser --- preset halo/Lyapunov entries
        by energy, click to load
  \item Manifold tube rendering: many semi-transparent trajectories,
        colour-coded by stable/unstable and $\pm$ branch
  \item Live Jacobi-constant readout in the footer (sanity check; drift
        diagnoses integration error or 4-body perturbation)
\end{itemize}

\subsection{Sequencing}

\begin{center}
\begin{tabular}{ll}
  \toprule
  4.1 \,\&\, 4.3 & foundational, independent, $\sim$2--3~d each \\
  4.2 (frame propagator) & needs 4.1; $\sim$1~d \\
  4.4 (Lagrange + Jacobi) & needs 4.3; $\sim$1~d \\
  4.5 (periodic orbits) & needs 4.4; $\sim$5--7~d (DC robustness) \\
  4.6 (manifolds) & needs 4.5; $\sim$3--4~d \\
  4.7 (transfers) & needs 4.6 + 4.2; $\sim$3~d \\
  4.8 (WSB diagnostic) & needs 4.6 + BCR4BP RHS; $\sim$4--5~d \\
  4.9 (visualization) & threads through all of the above; $\sim$3--4~d \\
  \midrule
  \textbf{Total} & \textbf{$\sim$5--6 weeks} \\
  \bottomrule
\end{tabular}
\end{center}

\subsection{Hard tradeoffs decided up front}

\begin{itemize}[leftmargin=*]
  \item \textbf{CR3BP vs full ephemeris}: do all family computation in
        pure CR3BP; refine into the SPICE-ephemeris model as a forward-
        shooting follow-up. Pure CR3BP first.
  \item \textbf{JAX vs SciPy for batch manifolds}: build on SciPy DOP853
        first to match the existing code path; expose a JAX
        \texttt{lax.scan} + \texttt{vmap} fast path under the \texttt{gpu}
        pixi feature in a follow-up.
  \item \textbf{Synodic-frame UI complexity}: do the inertial$\to$synodic
        transform on the backend (\texttt{output\_frame} in the request);
        renderer stays a dumb pipeline.
  \item \textbf{Discoverability}: add a small glossary section in the
        sidebar covering Jacobi, halo, manifold, WSB --- these terms are
        unusable to anyone outside the field.
  \item \textbf{BCR4BP scope}: only used by 4.8 (ballistic capture
        diagnostic). Don't try to do periodic orbits or generic
        propagation in BCR4BP --- CR3BP is enough everywhere else.
\end{itemize}

% ============================================================
%  PHASE 5 — Real star field & astro-navigation (NEXT)
% ============================================================
\newpage
\section{Phase 5 — Real Star Field \& Astro-Navigation}

\subsection{Goals}

Two intertwined deliverables:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Star field}: render a real celestial sphere from a standard
        astrometric catalogue so the background of the WebGPU scene shows
        the actual sky --- the same view a spacecraft camera would see.
  \item \textbf{Astro-navigation}: build the algorithms that real
        spacecraft use to determine attitude and position from that sky:
        star-tracker simulation, lost-in-space attitude solvers, optical
        landmark / planet-limb navigation, and a closed-loop ``navigate by
        stars'' demo that corrects a deliberately noisy propagator.
\end{enumerate}

These pair naturally: the star field is the rendering substrate, the
astro-nav layer is the application that uses it for a meaningful purpose.

\subsection{Pillar A --- Star catalogue \& renderer}

\subsubsection{5.1 Catalogue ingest}

Pull the Hipparcos catalogue (HIP, $\sim$118\,000 stars, magnitude limit
$\sim$12.5) and the Yale Bright Star Catalogue (BSC5, $\sim$9\,100 stars,
magnitude limit $\sim$6.5 --- the naked-eye sky).

\begin{itemize}[leftmargin=*]
  \item Download once via a manifest-driven script (mirroring
        \texttt{fetch\_kernels.py}); store the parsed binary in
        \texttt{data/stars/} as packed Float32 columns
        ($\alpha$, $\delta$, $V$, $B-V$, ID)
  \item Sha256-pin in \texttt{backend/oamp/stars/manifest.toml}
  \item Re-export as a compact bundle for the browser
        (\texttt{web/public/data/stars\_bsc5.bin}, $\sim$200\,KB)
\end{itemize}

\subsubsection{5.2 WebGPU star renderer}

\begin{itemize}[leftmargin=*]
  \item Point-sprite pipeline: each star is a single instanced quad
        coloured by $B-V$ via a Planckian colour-temperature lookup,
        sized by magnitude
  \item Stars sit at the camera-clip far-plane in the inertial frame, so
        they don't move with camera position (only orientation)
  \item Optional constellation outlines (88 IAU constellations) toggled
        via a footer pill
  \item Optional star labels for Bayer designations (greek letters) at the
        $\sim$50 brightest --- togglable; uses canvas-rendered text quads
  \item Magnitude-limit slider in the footer
        ($V_\text{lim} \in [-2, 7]$) lets the user dim the field for
        readability
\end{itemize}

\subsubsection{5.3 Bright movers}

Sun, Moon, planets are not in the star catalogue but should appear in the
same view. Pull positions from SPICE at the active trajectory's time, render
as small coloured discs sized by apparent magnitude, label them, and slide
their positions as the time scrubber moves --- so the user sees the Moon
crossing a constellation across a multi-day trajectory.

\subsection{Pillar B --- Astro-navigation algorithms}

\subsubsection{5.4 Star-tracker simulation}

Given a body-frame attitude quaternion $q_\text{B/I}$ and a tracker FOV
$\theta$, return the list of catalogue stars in the FOV with simulated
pixel coordinates and a noise model
($\sigma_\text{centroid} \sim 0.5\,$arcsec, optional bias).
Endpoint \texttt{POST /astro/tracker}:

\begin{verbatim}
{
  "q_bi":  [w, x, y, z],
  "fov_rad": 0.349,                # 20 deg
  "mag_limit": 6.0,
  "noise_arcsec": 0.5
} -> [{"hip_id", "ra", "dec", "mag", "pixel_x", "pixel_y"}]
\end{verbatim}

\subsubsection{5.5 Lost-in-space attitude solver}

Given a list of measured star pairs (pixel positions with no prior attitude
knowledge), determine attitude using one of two classic algorithms:

\begin{itemize}[leftmargin=*]
  \item \textbf{Triangle / pyramid}: compute pairwise inter-star angles,
        look up against a $K$-vector indexed catalogue, vote for the
        most-consistent attitude
  \item \textbf{Davenport q-method / QUEST}: from three or more identified
        stars, solve the Wahba problem for the best-fit attitude quaternion
\end{itemize}

Endpoint \texttt{POST /astro/identify} returns the matched stars and the
estimated attitude with a covariance.

\subsubsection{5.6 Optical landmark / planet-limb navigation}

When the spacecraft has prior attitude knowledge but unknown position:

\begin{itemize}[leftmargin=*]
  \item Render a planet from a known position using its SPICE-derived shape
        model; extract limb pixels
  \item Given measured limb pixels, recover line-of-sight to the planet
        centre, combine with parallax-against-stars and a coarse
        ephemeris prior, solve for spacecraft position
  \item This is what \emph{Deep Space~1}, \emph{Stardust}, and JAXA's
        Hayabusa missions all used (``AutoNav''-style optical navigation)
\end{itemize}

\subsubsection{5.7 Closed-loop ``navigate by stars'' demo}

Tie the pieces together:

\begin{enumerate}[leftmargin=*]
  \item Run a Phase~2 propagation as ground truth
  \item Add Gaussian process noise to the propagator state to simulate
        unmodelled dynamics
  \item At each ``measurement epoch'', simulate the star tracker (5.4)
        and an optical-navigation fix (5.6)
  \item Run an extended Kalman filter (EKF) that fuses the noisy
        propagator with the measurements to estimate state + covariance
  \item Render the truth orbit, the propagator estimate, and the
        EKF-corrected estimate as three overlaid trajectories with a
        $3\sigma$ uncertainty tube
\end{enumerate}

The point: showcase a real autonomous-navigation loop ending in a
sub-kilometre position covariance even when the propagator has been
deliberately broken --- the standard cislunar / deep-space navigation
demonstration.

\subsection{Pillar C --- Frontend integration}

\subsubsection{5.8 Sky toggle + sandbox}

\begin{itemize}[leftmargin=*]
  \item Header toggle: \emph{Sky} on/off (default on once Phase~5 ships)
  \item Footer: magnitude-limit slider, constellation toggle, label toggle
  \item ``Star-tracker view'' camera mode that snaps the camera to the
        spacecraft's body-frame $+Z$ axis with the configured FOV ---
        gives the user a literal look-through-the-tracker view, with the
        simulated noise overlay rendered as little crosshairs on each
        matched star
  \item Navigation-demo panel: choose a baseline trajectory, set noise /
        measurement rate, hit \emph{Run} and watch the 3-trajectory
        comparison stream in
\end{itemize}

\subsection{Sequencing}

\begin{center}
\begin{tabular}{L{5cm} C{2.5cm} L{5.5cm}}
  \toprule
  \textbf{Work item} & \textbf{Est.\ duration} & \textbf{Dependency} \\
  \midrule
  5.1 Catalogue ingest      & 2--3 days  & --- \\
  5.2 WebGPU star renderer  & 4--5 days  & 5.1 \\
  5.3 Bright movers (SPICE) & 1--2 days  & 5.2 + existing SPICE \\
  5.4 Star-tracker sim      & 2--3 days  & 5.1 \\
  5.5 Attitude solver       & 4--5 days  & 5.4 \\
  5.6 Limb navigation       & 4--5 days  & 5.2, 5.4 \\
  5.7 Nav demo + EKF        & 4--5 days  & 5.4, 5.6 \\
  5.8 Frontend integration  & 3--4 days  & all \\
  \midrule
  \textbf{Total}            & \textbf{4--5 weeks} & \\
  \bottomrule
\end{tabular}
\end{center}

\subsection{Hard tradeoffs decided up front}

\begin{itemize}[leftmargin=*]
  \item \textbf{Catalogue choice}: BSC5 (Yale Bright Star, $\sim$9\,K stars)
        for the rendered field --- big enough to look like the real sky,
        small enough to ship in the public folder. HIP for the tracker
        simulation if a user wants tighter FOVs at fainter magnitudes.
  \item \textbf{Constellation outlines}: render from the standard IAU
        88-constellation line list (Roger Sinnott's compilation); ship as
        a hand-curated JSON.
  \item \textbf{Time-dependence}: stars are treated as fixed at the J2000
        equator/equinox. Proper motion is in the catalogue but ignored
        for rendering; star-tracker simulation may apply it for missions
        spanning years.
  \item \textbf{No barycentric aberration} for the renderer (negligible at
        spacecraft velocities). The tracker simulation \emph{will} apply
        it when needed for sub-arcsecond residuals.
  \item \textbf{Attitude representation}: quaternions on the wire
        (always); DCM and Euler angles only inside specific algorithms.
\end{itemize}

% ============================================================
%  FUTURE / STRETCH GOALS — GR + other ambitious follow-ups
% ============================================================
\newpage
\section{Future / Stretch Goals}

These are not scheduled. They are deliberately ambitious targets that would
take OAMP from a Newtonian-with-CR3BP sandbox into territory currently
inhabited by JPL Monte, GMAT, FreeFlyer, and AGI/STK Premium.

\subsection{Stretch~A --- General Relativity}

The original Phase~5 plan, demoted to a stretch goal in favour of the
star-field / astro-nav phase. The work-breakdown below is preserved for
when an interested contributor takes it on.

\subsubsection{A.1 Post-Newtonian corrections (bridge)}

Additive accelerations on top of the existing DOP853 integrator, validated
against analytic results in the $c \to \infty$ limit and the canonical
solar-system PN benchmarks.

\begin{itemize}[leftmargin=*]
  \item \textbf{Schwarzschild (1PN)}: dominant solar-system GR effect,
        $\mathbf{a}_\text{Schw} = \tfrac{\mu}{c^2 r^3}\big[(4\tfrac{\mu}{r} - v^2)\mathbf{r} + 4(\mathbf{r}\!\cdot\!\mathbf{v})\mathbf{v}\big]$
  \item \textbf{Lense--Thirring} frame-dragging from the central body's
        angular momentum $\mathbf{S} = I_\oplus \boldsymbol{\omega}_\oplus$
  \item \textbf{de Sitter} geodetic precession from the solar barycentric
        motion of the Earth--spacecraft system
  \item \textbf{Tests}: Mercury perihelion 42.98$''$/century to $\pm$0.5\%;
        Gravity Probe~B geodetic 6606.1\,mas/yr to $\pm$1\%; Shapiro delay
        for Earth--Moon baseline; PN $\to 0$ as $c \to \infty$
\end{itemize}

\subsubsection{A.2 Full GR geodesic integrator}

DSX / Brumberg--Kopejkin BCRS metric:
$ds^2 = -(1 - 2w/c^2)c^2 dt^2 + (1 + 2w/c^2)\delta_{ij} dx^i dx^j + \mathcal{O}(c^{-4})$
with $w = \sum_A G M_A / r_A$ over solar-system bodies.

\begin{itemize}[leftmargin=*]
  \item 8D geodesic state $(t_\text{TDB}, x^\mu, u^\mu)$ integrated by
        DOP853, with $g_{\mu\nu}u^\mu u^\nu + c^2$ logged as a quality
        invariant
  \item Christoffel symbols computed analytically from the PN metric
        expansion --- no numerical differentiation
  \item Endpoint \texttt{POST /propagate/gr} accepts BCRS initial
        conditions and a coordinate-time span
\end{itemize}

\subsubsection{A.3 Tetrad thrust model}

Convert body-frame thrust commands to the local orthonormal tetrad
$e^\mu{}_{(a)}$ built from $u^\mu$ and the attitude quaternion; inject as
the right-hand side of the non-geodesic equation $Du^\alpha/d\tau = f^\alpha$.

\subsubsection{A.4 Metric pre-bake cache (Ray)}

Live SPICE-driven $w(\mathbf{r}, t)$ evaluation is $\sim$100$\times$ slower
than Newtonian propagation. A Ray actor pool samples $w$ and its spatial
gradients on a Cartesian grid over the mission window, stored as HDF5 in
\texttt{data/metric\_cache/} with a SHA256 manifest pinning the SPICE
kernels used at bake time.

\subsubsection{A.5 Frontend}

GR vs PN vs Newton three-way overlay, residual panel showing
$|\mathbf{r}_\text{GR} - \mathbf{r}_\text{Newton}|(t)$, proper-time $\tau$
readout alongside coordinate time, optional 2D equatorial slice of the
Newtonian potential as a heatmap underlay.

\subsection{Stretch~B --- Tesseral gravity}

Beyond the zonal $J_n$, the $C_{nm}, S_{nm}$ tesseral harmonics matter for
GEO station-keeping (the $75^\circ$E and $105^\circ$W gravitational wells),
Earth--Moon mascon flybys, and any sub-kilometre precision orbit
determination on a non-spherical body. EGM2008 / GRGM1200A coefficients
are public.

\subsection{Stretch~C --- Ground-track \& visibility analysis}

\begin{itemize}[leftmargin=*]
  \item Project the trajectory onto an equirectangular Earth map; mark
        ascending / descending nodes
  \item Ground-station catalogue + line-of-sight pass prediction with
        elevation / azimuth windows
  \item Eclipse map: Earth and Moon shadow cones intersected with the
        trajectory, with umbra / penumbra distinction
  \item Sun-angle windows for solar-array sizing
\end{itemize}

\subsection{Stretch~D --- Conjunction analysis}

Against a TLE catalogue (Celestrak active satellites + debris): closest-
approach distances over a 7-day prediction window, probability of collision
under a 1$\sigma$ covariance model, sortable risk list. This is the core
service Combined Space Operations Centre (CSpOC) sells to operators.

\subsection{Stretch~E --- Multi-spacecraft \& constellation propagation}

Propagate $N$ spacecraft jointly, render coverage maps over a target
region, plot constellation health (gap analysis, mean revisit time).
Walker / Flower / Star-of-stars constellation generators as preset
buttons.

% ============================================================
%  LET YOUR CREATIVITY GO WILD
% ============================================================
\newpage
\section{Let Your Creativity Go Wild}

These are not roadmap items. They are deliberately open-ended ideas where
the only design constraint is ``it should be cool.'' Pick one, build it,
open a PR. Add new ideas as they occur to you.

\subsection{Cinematic \& storytelling modes}

\begin{itemize}[leftmargin=*]
  \item \textbf{Tour mode} --- auto-fly the camera through canonical
        historical missions (Apollo~11 TLI; Voyager~2 Jupiter encounter;
        Hayabusa~2 touchdown; JWST L$_2$ insertion; Hiten ballistic
        capture) with synchronised captions and timeline annotations
  \item \textbf{Procedural mission cinematography} --- render a 60-second
        MP4 from any user trajectory with camera moves, captions, and a
        music bed selected from BPM-matched royalty-free libraries
  \item \textbf{Mission narrative export} --- pull a 2-paragraph trip
        summary from the propagator data: ``departed LEO 2026-01-04
        17:30Z, performed a 3.1\,km/s TLI burn, encountered the lunar
        SOI 4.2 days later...''
\end{itemize}

\subsection{Live data \& real-world coupling}

\begin{itemize}[leftmargin=*]
  \item \textbf{Live-ISS mode} --- pull the current ISS TLE every few
        hours; render its present position with a sun-illumination
        indicator and the orbital ground track of the next six passes
  \item \textbf{AR through your phone} --- point the camera at the night
        sky; overlay predicted satellite paths and the OAMP-rendered
        spacecraft on the live video feed
  \item \textbf{Live debris catalogue} --- render the $\sim$25\,000
        TLE-tracked objects as a particle cloud; click any one for
        identification, mass, country of origin
  \item \textbf{Solar-weather coupling} --- pull NOAA F10.7 and Kp live;
        show their effect on MSIS drag in a side panel
\end{itemize}

\subsection{Generative \& AI-augmented}

\begin{itemize}[leftmargin=*]
  \item \textbf{Natural-language trajectory designer} --- ``get me to
        Europa for under 5\,km/s'' driving the solver chain via an LLM
        with tool access to Hohmann, Lambert, multi-burn NLP, and CR3BP
        manifold endpoints
  \item \textbf{Mission archetype templates} --- LLM-generated starter
        scenarios (``cubesat constellation for L-band Earth observation'';
        ``2030 manned Mars opposition class''); user tunes the result
  \item \textbf{Anomaly detection} --- an ML model that, given a
        propagated trajectory and a mission objective, flags maneuvers
        that are dominant cost drivers and suggests alternatives
\end{itemize}

\subsection{Wild physics / alternate sandboxes}

\begin{itemize}[leftmargin=*]
  \item \textbf{Alternate-physics sandbox} --- ``what if $G$ was 2$\times$?'';
        ``what if the Moon weren't there?''; ``what if Mercury orbited
        with PN turned off?'' Change the constants, re-propagate, watch
        the orbit drift
  \item \textbf{Lyapunov-spectrum visualiser} --- colour each piece of
        synodic-frame state space by its local Lyapunov exponent;
        chaotic regions around $L_3$ become visually obvious
  \item \textbf{N-body chaos sandbox} --- drop $N$ point masses with
        arbitrary positions / velocities, integrate, render the chaotic
        evolution and a Poincar\'e section
  \item \textbf{Light-sail / electric-propulsion} --- low-thrust
        spiralling with shape-based methods; tightly coupled to a power
        model that follows SRP shadow and orientation
  \item \textbf{Interstellar trajectory mode} --- Voyager-style outbound
        with PN-corrected acceleration tables; render the trajectory
        through the heliopause
\end{itemize}

\subsection{New audiences \& interfaces}

\begin{itemize}[leftmargin=*]
  \item \textbf{WebXR mode} --- view the scene in a VR headset; reach
        into the orbit and drag the spacecraft node to retime a maneuver
  \item \textbf{Audio synthesis} --- drive a synth from orbital
        frequencies, eccentricity modulation, eclipses-as-amplitude.
        Kepler's ``music of the spheres'' but literal
  \item \textbf{Deep-field renderer} --- JWST-style starfield with
        diffraction spikes, rendered when the camera looks away from any
        solar-system body. Optionally include nebulae (Hubble HST
        composites) as static panoramas
  \item \textbf{Multiplayer mode} --- multiple users edit the same
        mission plan in real time (CRDT-backed editor state); chat
        sidebar with annotations pinned to orbit segments
  \item \textbf{Speedrun mode} --- ``land a payload in low lunar orbit
        in the minimum number of clicks''; leaderboard of optimised
        mission plans by total $\Delta v$, by time, by number of burns
\end{itemize}

\subsection{Asteroid \& deep-space}

\begin{itemize}[leftmargin=*]
  \item \textbf{Asteroid-mining sandbox} --- pull JPL Horizons NEAs,
        plan rendezvous, return-trajectory $\Delta v$ budgets, payload
        mass fractions, accumulated regolith mass returned per dollar
        of fuel
  \item \textbf{Defending Earth} --- given an inbound NEA on a hazardous
        approach, design a kinetic-impactor mission within a 12-month
        window; visualise the deflection cone of resulting orbits
  \item \textbf{Hayabusa-replica autonav} --- close the loop end-to-end:
        propagate truth, simulate the optical-nav fix on the asteroid
        limb, fuse with the EKF (Phase~5), execute the touch-and-go
\end{itemize}

\subsection{In-browser optimisation playground}

\begin{itemize}[leftmargin=*]
  \item Drag a target marker around the 3D scene; watch the multi-burn
        NLP re-solve in real time with a colour gradient on the
        trajectory encoding $|\Delta v|$ density
  \item Pareto-front explorer --- plot $\Delta v$ vs.\ time-of-flight for
        a swept Lambert / patched-conic transfer; click any point to
        load the corresponding trajectory
  \item Sensitivity heatmap --- perturb each design variable by
        $1\sigma$; render the resulting trajectory bundle as a translucent
        tube
\end{itemize}

The point of this section is to keep the imagination ahead of the
schedule. Every shipped roadmap phase started in a list like this.

% ============================================================
%  OVERALL TIMELINE
% ============================================================
\newpage
\section{Overall Timeline}

\subsection{Phase comparison}

\begin{center}
\rowcolors{2}{rowalt}{white}
\begin{tabularx}{\textwidth}{L{2.6cm} X X X X X}
  \rowcolor{tabhead}
    & \color{white}\textbf{P1}
    & \color{white}\textbf{P2}
    & \color{white}\textbf{P3}
    & \color{white}\textbf{P4}
    & \color{white}\textbf{P5} \\
  Physics
    & Newton + $J_2$
    & Newton + $J_2$\,\dots\,$J_6$ + drag + SRP + 3B
    & = P2 (no new physics)
    & CR3BP + BCR4BP
    & = P4 (no new physics) \\
  Frames
    & J2000
    & J2000
    & + body selector (Earth/Moon)
    & + EM synodic
    & + body-frame attitude (quaternions) \\
  Integrator
    & DOP853
    & + Verlet + Yoshida-4
    & = P2
    & = P2 (CR3BP non-dim)
    & = P4 \\
  Optimisers
    & ---
    & Lambert + Hohmann + CasADi NLP
    & all four exposed in sidebar; + TLE ingest
    & + diff.\ correction (Lyapunov)
    & + Wahba / QUEST attitude solver; EKF \\
  Frontend
    & 3 demo scenes
    & Maneuver editor + scrubber
    & Solver panel, Moon render, cislunar demo, apse markers, altitude chart, camera targeting
    & Frame selector, $L_n$ markers, Lyapunov + manifold + WSB panels, animated play/pause, past-solid/future-dashed split, coastline overlay
    & Real celestial sphere, constellations, planet movers, star-tracker view, nav-demo 3-trajectory overlay \\
  Heavy compute
    & ---
    & Ray streaming
    & ---
    & ---
    & --- \\
  Status
    & \emph{shipped}
    & \emph{shipped}
    & \emph{shipped}
    & \emph{shipped}
    & next, $\sim$4--5 weeks \\
\end{tabularx}
\end{center}

\subsection{Critical path}

\begin{center}
\begin{minipage}{0.85\textwidth}
\begin{verbatim}
   P1 ──► P2 ──► P3 ──► P4 ──► P5 (star field + astro-nav)
                                   │
                                   └──► Stretch A: PN + GR
                                        Stretch B: tesseral gravity
                                        Stretch C: ground tracks
                                        Stretch D: conjunction analysis
                                        Stretch E: constellations
\end{verbatim}
\end{minipage}
\end{center}

Phase~5 is the immediate next deliverable.  The Stretch~A--E follow-ups are
independent of each other and can be picked up by different contributors
once Phase~5 ships.  GR (Stretch~A) is the most physically ambitious; the
others are scoped tightly enough to be one-contributor weekend projects.

% ============================================================
%  CONVENTIONS REFERENCE
% ============================================================
\section{Conventions Reference}

\begin{center}
\begin{tabularx}{\textwidth}{L{3cm} X}
  \toprule
  \textbf{Convention} & \textbf{Value} \\
  \midrule
  Licence        & AGPL-3.0 (network-service source-disclosure obligation; switched from Apache-2.0 during Phase~4 polish) \\
  Time on wire   & UTC ISO-8601 string \\
  Time internal  & TDB seconds since J2000 (= SPICE ET); see \texttt{oamp.timescales} \\
  Units          & SI throughout the engine (m, m/s, kg, s) \\
  Accelerator    & JAX (pixi \texttt{gpu} feature); CPU default \\
  Heavy compute  & Ray (pixi \texttt{full} feature) \\
  SPICE kernels  & Pinned by SHA256 in \texttt{backend/oamp/spice/manifest.toml}; \emph{tracked in-tree} since the data-bundling pass so fresh clones run without network fetches \\
  Coastline data & Natural Earth 110m, tracked at \texttt{web/public/data/} \\
  Epoch J2000    & 2000-01-01T11:58:55.816Z UTC \\
  $TT - TAI$     & $32.184\,$s (fixed by IAU) \\
  \bottomrule
\end{tabularx}
\end{center}

\end{document}
